### 2017-10-15 mcmc.tex
tweaks

Finally---and perhaps most importantly---a magical property of a sampling
  (in a $D$-dimensional space)
  is that if some of your $D$ dimensions are totally uninteresting
  (nuisance parameters, if you will)
  and some of your $D$ dimensions are of great interest,
  the sampling in the full $D$-space is trivially converted into a sampling in the subspace of interest:
You just drop from each $\pars_k$ vector (or blob or list) the dimensions of no interest!
That is, the projection of the sampling to the subspace of interest produces
  a sampling of the marginalized pdf, marginalizing (or projecting) out the nuisance parameters.%
  \note{This point about marginalization is, once again, a use of the sampling to perform an \emph{integral};
        the marginalized pdf is obtained from the full pdf by an integration.
        The sampling performs this integration automatically.}
That is extremely important for inference,
  where there are always parameters with very different levels of importance to the scientific conclusions.
This point will return again below (\sectionname~\ref{sec:results}).

>>>>

Finally---and perhaps most importantly---a magical property of a sampling
  (in a $D$-dimensional space)
  is that if some of your $D$ dimensions are totally uninteresting
  (nuisance parameters, if you will)
  and some of your $D$ dimensions are of great interest,
  the sampling in the full $D$-space is trivially converted into a sampling in the subspace of interest:
You just drop from each $\pars_k$ vector (or blob or list) the dimensions of no interest!
That is, the projection of the sampling to the subspace of interest produces
  a sampling of the marginalized pdf, marginalizing (or projecting) out the
  nuisance parameters.\note{This point about marginalization is, once again,
        a use of the sampling to perform an \emph{integral};
        the marginalized pdf is obtained from the full pdf by an integration.
        The sampling performs this integration automatically.}
That is extremely important for inference,
  where there are always parameters with very different levels of importance to the scientific conclusions.
This point generalizes from a subspace to any function of the parameters;
and it will return again below (\sectionname~\ref{sec:results}).
